\cvsection{Experience}
\begin{cventries}
  \cventry
    {\textbf{Full Stack Web Developer} | Facility Maintenance}
    {Intelligent Data Systems}
    {Williston Park, NY}
    {January 2016 - Present}
    {
      \begin{cvitems}
      	\item {Design, implement, test, deploy, and support SAAS and enterprise web applications across the web stack using SQL Server, ASP.NET MVC, and JavaScript.}
        \item {Develop mobile applications using web technologies via Apache Cordova and their supporting APIs.}
        \item{Maintain SQL Server instances creating tables, stored procedures, triggers and managing the deployment of database updates.}
        \item{Develop integrations with well-known technology providers like QuickBooks and Avalara as well as other industry partners}
      \end{cvitems}
    }
  \cventry
    {\textbf{Engineering Leadership Development Program}}
    {BAE Systems}
    {Endicott, NY}
    {January 2015 - Present}
    {
      \begin{cvitems}
      	\item {Lead a team of peers through an internal RFP process to redesign an engine control subsystem.}
        \item {Attended quarterly leadership training and annual leadership development conferences.}
      \end{cvitems}
    }
  \cventrytwo
    {\textbf{Firmware Engineer} | Engine Control Systems}
    {BAE Systems}
    {Endicott, NY}
    {January 2016 - Present}
    {
      \begin{cvitemstwo}
        \item{Reshaped the requirements, design, implementation, and test of a dual-core, real-time operating system which manages partitioned application software.}
        \item{Adapted an existing bootloader to comply with changes in the communication and upload protocols.}
        \item{Adhered to common communication standards such as TFTP, SNMP, ARINC 615A-2, ARINC 665, ARINC 664 (AFDX).}
      \end{cvitemstwo}
    }
  \cventrytwo
    {\textbf{Field Reliability Engineer} | Commercial Avionics}
    {BAE Systems}
    {Endicott, NY}
    {January 2015 - January 2016}
    {
      \begin{cvitemstwo}
        \item {Investigated failures in revenue service. Used product return data, design documentation, test data, fault storage, and failure analysis to determine root cause and corrective action.}
        \item {Created several process improvements including the formation of a formal investigation process and a fault data parser. Lead the transition to a new project management tool.}
      \end{cvitemstwo}
    }
  \cventry
    {\textbf{Firmware Engineer} | Thermal Printing}
    {CognitiveTPG}
    {Ithaca, NY}
    {June 2014 - January 2015}
    {
      \begin{cvitems}
        \item {Designed, implemented, and tested software which integrates into large, real-time systems.}
        \item {Used common communication protocols such as Bluetooth, Wi-Fi, TCP/IP, SPI, I2C, and RS-232.}
      \end{cvitems}
    }
\end{cventries}